Make any stupid plot you want

### 2020-11-24 draft/sections/math.tex
msotly notes on what I need to add/make

\section{Notation \& Definitions}

@@

\subsection{Data Space}
\begin{figure}[ht]
    \includegraphics[width=0.5\linewidth]{figures/sections/math/mobius.png}
    \caption{write up some words here}
    \label{fig:mobius}
    %%possibly replace w/ simpler deconstructed band image notes-11-19-20
\end{figure}

We use a fiber bundle model to represent the data, as proposed by Butler 
\cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}.

One example of a fiber bundle is the mobius band shown in figure~\ref{fig:mobius}. A fiber bundle is a topological total space $E$ with an embedded fiber space $F$, a base space on which the fibers lie $K$ and the $\pi$ and $\sigma$ mappings between $E$ and $K$. The space of all $\sigma$ is $\Gamma$

\begin{tikzcd}
    F \arrow[r, hook] & E \arrow[d, "\pi" description, bend right ] \\
                      & K \arrow[u, "\sigma" description, bend right]
\end{tikzcd}

As illustrated by the mobius band example in figure~\ref{fig:mobius}, the vertical lines $F$ are the range of possible values embedded in $E$. The circle $K$ is a representation of the connectivity of the points in $E$. The function $\pi$ is the mapping from a point on a specific fiber $F_{k}|k\in K$ in $E$ to a location $k \in K$.?  
The section $\sigma$ is the mapping from locations $k$ on $K$ to points on $F_{k}$ in $E$.  (Pull this back into more specific about fig, the general is making this more confusing.)

\subsubsection{Base Space $K$}

@@

One way to represent the topological space K is as a set composed of simplices, such as those shown in figure~\ref{fig:simplex}. Simplices are a way of encoding the connectivity of each observation ($\sigma(k)$) to another:

\begin{description}
    \item[0-simplex] discrete observations (inventory records)
    \item[1-simplex] 1D continuos data (timeseries)
    \item[2-simplex] 2D continuos data (map)
    \item[3-simplex] 3D continuos data (video)
\end{description}

In a locally trivial fiber bundle $E = F \times K$, it can be assumed that all $F_{k}$ for $k \in K$ are equal. A fiber bundle can be made locally trivial by approximating the total space E as a simplacial complex.

\subsubsection{Fiber Space $F$}
The fibers encode the set of all possible values each observation can take.  Spivak's formulation is that the fibers encode the union of the types of measurements\cite{spivakSIMPLICIALDATABASES}. For example, given the section $\Gamma(mobuis strip) =
\{\sigma_1=\sin, \sigma_2=\cos\}$:
%%fill in more spivak
the fiber $F = \{float, float\}$.

%%% mapping from measurement back to type is the basis for gaurateening invariance

\subsubsection{Subset \& Streaming}
$\Gamma(E)$ is the space of all points in $F$ returned by $\sigma$; therefore the points being visualized in a streaming or animation example can be considered a subset that lives on base space $U$ embedded in $K$ with the same fiber $\iota^*E$ and $\iota^*\sigma$.

@@

\subsection{Display Space}
\label{sec:display}
\begin{figure}[h]
    \includegraphics[width=.4\linewidth]{figures/sections/math/render.png}
    \caption{}
    \label{fig:render}
\end{figure}

@@

\subsection{Artist}
\begin{equation}
    A: \Gamma(E) \rightarrow \Gamma(H)
\end{equation}

>>>>

\section{Notation \& Definitions}
%%% add some words around

@@

%% E is a locally trivial fiber bundle over K where K is triangulizable space representing data space & H is a fiber bundle over S which is a simplacial complex of triangles representing visual space and artists in matplotlib will go between the two. E is a trivial fiber bundle $E = F \times K$, it can be assumed that all $F_{k}$ for $k \in K$ are equal.

\subsection{Data Model}
\begin{figure}[ht]
    \caption{write up some words here}
    \label{fig:fiberbundle}
    %%possibly replace w/ simpler deconstructed band image notes-11-19-20
    %% or replace w/ box w/ thing that's kind of convoluted 
    %% simpler still replace w/ timeseries of temp, 1D fiber
\end{figure}

%%% preface w/ we care about topology & types. 
We use a fiber bundle model to represent the data, as proposed by Butler 
\cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}.

One example of a fiber bundle is shown in figure~\ref{fig:mobius}. A fiber bundle is a topological total space $E$ with an embedded fiber space $F$, a base space on which the fibers lie $K$ and the $\pi$ and $\sigma$ mappings between $E$ and $K$.

\begin{tikzcd}
    F \arrow[r, hook] & E \arrow[d, "\pi" description, bend right ] \\
                      & K \arrow[u, description, bend right]
\end{tikzcd}

As illustrated by figure~\ref{fig:mobius}, the vertical lines $F$ are the range of possible values embedded in the total space $E$. The topol $K$ is a representation of the connectivity of the points in $E$. The function $\pi$ is the mapping from a point on a specific fiber $F_{k}|k\in K$ in $E$ to a location $k \in K$. 
The section $\sigma$ is the mapping from locations $k$ on $K$ to points on $F_{k}$ in $E$.
%%% include diagram here of formal definition of sigma

The space of all $\sigma$ is $\Gamma$  (Pull this back into more specific about fig, the general is making this more confusing.)
%% locally trivial - for every point in K there exists an open set neighborhood $U$ such that if you restrict E to that point, then  \iota*E = F\times U [maybe do mobius strip diagram here? U is subsection of the ring, part where it's not twisted. there exists a triangulation & a way to do so is simplicies

\subsubsection{Base Space $K$}
%% general statement about topology, examples of 0, 1, ....Ks [none triangular things, square/torus, ....], condition on K is that it can be represent as a triangulation of K (can be realized as triangle on K - extra structure that may be arbitrary

@@

%% k is a triangularizable topological space 
One way to represent the topological space K is as a set composed of simplices, such as those shown in figure~\ref{fig:simplex}. Simplices are a way of encoding the connectivity of each observation ($\sigma(k)$) to another: %%formula for simplacial complexes/simplacial sets

% replace this table w/ a diagram that shows this 
\begin{description}
    \item[0-simplex] discrete observations (inventory records)
    \item[1-simplex] 1D continuos data (timeseries)
    \item[2-simplex] 2D continuos data (map)
    \item[3-simplex] 3D continuos data (video)
\end{description}

I

\subsubsection{Fiber Space $F$}
\begin{figure}
    \includegraphics{}
    \label{fig:movie}
\end{figure}
%%% might 
The fibers encode the set of all possible values each observation can take. For example, the fiber bundle in figure~\ref{fig:movie} is the set of all possible movies, where each $k \in K$ is a frame in the movie. Each \sigma

which in Spivak's formulation means the fibers encode the union of the types of measurements\cite{spivakSIMPLICIALDATABASES}. Spivak also provides a way to map from

\subsubsection{Subset}
$\Gamma(E)$ is the space of all points in $F$ returned by $\sigma$; therefore the points being visualized in a streaming or animation example can be considered a subset that lives on base space $U$ embedded in $K$ with the same fiber $\iota^*E$ and $\iota^*\sigma$.

@@

\subsection{Prerender Space}
\label{sec:display}

% preamble type intro to displays, examples - displays can include screen, 3D printer, sphereical display, H is the total space of the screen. 11
\begin{figure}[h]
    \includegraphics[width=.4\linewidth]{figures/sections/math/render.png}
    \caption{}
    \label{fig:render}
\end{figure}

@@

%%%pho is paramterized over alpha, beta, which is obtained via pullback lookup from (Hx,Hy)-?(alpha, beta)

\subsection{Artist}
%% include some words about motivation 
\begin{equation}
    A: \Gamma(E) \rightarrow \Gamma(H)
\end{equation}
